Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2013-03-31 paper/ieee/oldpaper.tex
added ieee paper

\nocopyright
\frenchspacing
\pdfinfo{
/Title (Classification of Tweets by Company)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\author{
Curtis Ullerich, Daniel Stiner, Brandon Maxwell\\
Department of Computer Science and Engineering\\
Iowa State University
Ames, Iowa, USA\\
\{curtisu,stiner,bmaxwell\}@iastate.edu\\
}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusion of current trends. It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products. Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or merely contain keywords related to the company. Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
%Classification purely by keyword filtering often suffers from a
%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations. Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products. The other 36\% do not, but still contain keywords related to the company. Preliminary results have shown increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.\\
\end{quote}
\end{abstract}

>>>>

\nocopyright
\frenchspacing
\pdfinfo{
/Title (Classification of Tweets by Company)
}
\setcounter{secnumdepth}{0}  
\begin{document}

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusion of current trends. It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products. Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or merely contain keywords related to the company. Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
%Classification purely by keyword filtering often suffers from a
%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations. Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products. The other 36\% do not, but still contain keywords related to the company. Preliminary results have shown increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.\\
\end{quote}
\end{abstract}

### 2013-03-31 paper/ieee/paper.tex
added ieee paper

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusion of current trends. It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products. Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or merely contain keywords related to the company. Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
%Classification purely by keyword filtering often suffers from a
%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations. Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products. The other 36\% do not, but still contain keywords related to the company. Preliminary results have shown increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.\\
\end{quote}
\end{abstract}

\section{Introduction}
Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on user sentiment (\citeauthor{Ruiz}) and identifying characteristics of Twitter users (\citeauthor{conf/icwsm/PennacchiottiP11}) to tracking political protests and uncovering scams (\citeauthor{ICWSM101540}).
In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to obtaining meaningful results. Use of hashtags and username references on Twitter through syntax conventions (prepending with \# and @, respectively) can be used to select a subset of the tweets about a particular topic.

@@

We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. Data sets and scripts used for processing text data are available on the project website.\\
 (http://tweets.curtisullerich.com/)\\

@@

\section{Individual Contributions}
Specific team member contributions follow from what we originally stated in our project proposal. Brandon implemented utilities to push and pull tweets from our database in Java. He also researched about and wrote different Pipes that could be used by Mallet to transform the tweets during training. Brandon architected the project structure, and helped edit the project's paper and website. Curtis integrated Mallet into the project, prototyped the testing utilities, and wrote the JsonTweetIterator. He also wrote the majority of the paper, implemented the Twitter-aware tokenizer, and wrote bash scripts to process corpora for testing and analysis. Dan harvested tweets from Twitter and managed a database to store all our content. He designed and implemented the testing utility to compare all combinations of Pipes. Dan performed the statistical analysis and generated the graphs for the paper.\\

We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.

\section{ Acknowledgments}
Thank you to Dr. Jin Tian and our class teaching assistant, Ru He, for their helpful guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.

>>>>

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\maketitle

\tableofcontents

\vspace{10 mm}
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusion of current trends. It can also present a goldmine of useful data for businesses seeking to discover public opinion. Using machine learning techniques, we disambiguate the classification of tweets based on the presence company-specific keywords. Tweets present interesting classification challenges due to irregular formatting and sparsity of features. 
We survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations. Preliminary results show increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.
\end{quote}
\end{abstract}
\section{Introduction}
Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on user sentiment (\citeauthor{Ruiz}) and identifying characteristics of Twitter users (\citeauthor{conf/icwsm/PennacchiottiP11}) to tracking political protests and uncovering scams (\citeauthor{ICWSM101540}).
In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to obtaining meaningful results. Use of hashtags and username references on Twitter through syntax conventions (prepending with \# and @, respectively) can be used to select a subset of the tweets about a particular topic.

@@

We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. Data sets and scripts used for processing text data are available on the project website.\\
 (URL withheld per submission guidelines)\\

@@
